---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

The [R](http://www.r-project.org/) package `"binomial"` is an implementation for examining and summarizing statistics related to probabilities of number of successes in a fixed number of random independent and identically distributed trials. It also provides relevant visualizations of the binomial distribution.

* `bin_choose()` calculates the number of combinations of `k` successes in `n` trials.
* `bin_probability()` calculates the probability of `success` successes in `trials` trials with probability = `prob`.
* `bin_distribution()` creates a dataframe for the probability of each number of successes with probability = `prob` in `trials` trials. `plot()` show a plot of a binomial probability distribution
* `bin_cumulative()` creates a dataframe for cumulative probability of each success with probability = `prob` in `trials` trials. `plot()` show a plot of a binomial cumulative distribution.
* `bin_variable()` generates a binomial random variable object. `summary()` summarizes statistics of a binomial random variable.
* `bin_mean()` calculates the mean of a binomal distribution.
* `bin_variance()` calculates the variance of a binomal distribution.
* `bin_mode()` calculates the mode of a binomal distribution.
* `bin_skewness()` calculates the skewness of a binomal distribution.
* `bin_kurtosis()` calculates the kurtosis of a binomal distribution.



## Installation

Install the development version from GitHub via the package `"devtools"`:

```{r}
# development version from GitHub:
# install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-christinajin01/binomial")
# install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-christinajin01/binomial", 
                         build_vignettes = TRUE)
```



## Usage

```{r}
library(binomial)

# finds number of combinations of 2 successes in 5 trials
bin_choose(5, 2) 

# calculates probability of getting 2 successes in 5 trials (assuming prob of success = 0.5) 
bin_probability(2, 5, 0.5)

# finds binomial distribution in 5 trials (assuming prob of success = 0.5)
dis1 <- bin_distribution(5, 0.5)
dis1

# plots binomial probability distribution
plot(dis1)

# finds binomial cumulative distribution in 5 trials (assuming prob of success = 0.5)
dis2 <- bin_cumulative(5, 0.5)
dis2

# plots binomial cumulative distribution
plot(dis2)

# generates a binomial random variable object
bin1 <- bin_variable(10, 0.3) 
bin1

# summarizes the statistics of a binomial random variable
binsum1 <- summary(bin1)
binsum1
```


## Functions of measures
The following functions contain the important statistics of a binomial distrbution for mean, variance, mode, skewness, and kurtosis.

```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
