---
title: "Getting Started with Binomial Distribution"
author: "Christina Jin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial distribution}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Distribution
The package `"binomial"` is an implementation for examining and summarizing statistics related to probabilities of number of successes in a fixed number of random independent and identically distributed trials. It also provides relevant visualizations of the binomial distribution.


## Binomial Functions
- `bin_choose()` calculates the number of combinations of `k` successes in `n` trials.
```{r}
bin_choose(n = 5, k = 2)
```


- `bin_probability()` calculates the probability of `success` successes in `trials` trials with probability = `prob`.
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```


- `bin_distribution()` creates a dataframe for the probability of each number of successes with probability = `prob` in `trials` trials.

- `plot()` show a plot of a binomial probability distribution
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
plot(dis1)
```


- `bin_cumulative()` creates a dataframe for cumulative probability of each success with probability = `prob` in `trials` trials.

- `plot()` show a plot of a binomial cumulative distribution.
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
plot(dis2)
```


- `bin_variable()` generates a binomial random variable object.

- `summary()` summarizes statistics of a binomial random variable.
```{r}
bin1 <- bin_variable(trials = 10, prob = 0.3)
bin1
binsum1 <- summary(bin1)
binsum1
```


- Functions of measures: The following functions contain important statistics of a binomial distrbution for mean, variance, mode, skewness, and kurtosis.

```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
